\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-13 notes/2loopNLSM.tex
Finished CK boostrap 2nd pass

\def\tree{{\rm tree}}
\def\pol{\varepsilon}
\def\Tr{\, {\rm Tr}}
\def\tr{\, {\rm tr}}
\def\eps{\varepsilon}
\def\e{\varepsilon}
\def\ep{\varepsilon}
\def\SYM{MSYM}
\def\nn{\nonumber}
\def\Neqfour{{{\cal N}=4}}
\def\NeqFour{{{\cal N}=4}}
\def\Neqeight{{{\cal N}=8}}
\def\NeqEight{{{\cal N}=8}}
\def\NeqOne{{{\cal N}=1}}
\def\Fact{{\cal F}}
\def\f{\widetilde f}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\def\Ksl{{\s K}}
\def\ksl{\s{k}}
\def\Perm{{\cal P}}
\def\M{{\cal M}}
\def\ve{\varepsilon}
\def\tlambda{{\tilde\lambda}}
\def\MHVbar{$\overline{\hbox{MHV}}$}
\def\NMHVbar{$\overline{\hbox{NMHV}}$}
\def\P{{\rm P}}
\def\NHP{{\rm NHP}}
\def\mud{\lambda}
\def\bowtie{{\rm bow\mbox{-}tie}}
\newcommand{\cred}{\bf \color{red}}
 \newcommand{\cblue}{\color{blue}}
\newcommand{\andd}{\ , \quad \text{and}  \quad}
\newcommand{\forr}{\ , \quad \text{for}  \quad}

%TODO-type commands
\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed:#1]]}}
\newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}

@@

Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
The four conditions imposed on the ansatz are summarized here and elaborated on below.
\begin{enumerate}
\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
The diagram numerators are only a function of the diagram's topology and labeling.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
\end{enumerate}

@@

The kinematic numerators need to be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
Insisting on a local numerator is partly a matter of convenience as the ansatz for a rational function would quickly grow out of control without a guiding principle for what terms to include.
Locality is also physically motivated since Feynman rules typically produce polynomial numerators.
While locality is well motivated from a physical and computational standpoint, the literature has featured numerators that violate locality, break manifest Lorentz invariance, and modify naive power counting through the presence of higher spin modes \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}. \jm{Alex wrote some of this citation.  I'm not sure why it broke.}
These developments suggest that relaxing locality is a viable option when the condition proves too stringent for an ansatz.
We will comment more on locality in \sect{}.

@@

Somewhere emphasize that Zvi et al didn't do the most general ansatz, imposed extra loop power counting constraints.

Different kinds of CK.  We want global.  Global is the simplest
option, it is also the option that you would automatically get if you
had a color-dual Lagrangian.  By ``global'' we mean that
color-kinematics duality is satisfied in any kinematic configuration
of the integrand.  This is a much more stringent condition than
absolutely necessary.  There is reason to believe \cite{Bern:2015ooa} that global numerators cannot
always be found.  One resolution to the issue is to only demand
color-kinematics duality on the unitarity cuts of the integrand, i.e.,
in specific kinematic limits.  Enforcing Jacobi on the cuts is enough
to ensure that the squared integrand will correctly cut to gravity (or
whatever the squared theory might be).  When a globally color-dual
numerator cannot be found, another alternative explored in the
literature is to increase the size of the numerator ansatz by
enlarging the numerator from a polynomial to a rational function with
spurious singularities (cite Donal et al).  When global
color-kinematics fails, the hope is that it can be restored by
enlarging the size of the ansatz, either by giving the numerator of
each graph its own ansatz (first option described) or by promoting the
numerator to a non-local function (second option described).  Note
that a theory whose Lagrangian has color-kinematics duality would
naturally produce a globally color-dual integrand so the quest for a
global numerator is closely related to the existence of a Lagrangian
exhibiting color-kinematics duality.  Section X is devoted to
color-dual representations of the 4pt 2-loop NLSM integrand and the
analogous integrand for YM is treated in section Y.  Two-loop
color-dual integrands for pure YM have been investigated before but
only for a limited ansatz that manifests locality \cite{Bern:2015ooa}.  All of the N=4 SYM constructions below 5-loop are local.
Mention generalized double copy.

Color-kinematics duality is stated in terms of cubic graphs so the
first step is to express in the integrand in terms of such graphs.  As
an example we will focus on the 4pt 2-loop integrand of some
color-dual theory like NLSM or YM.  The 4pt 1-loop integrand is not a
sufficiently illustrative example because, for instance, it lacks any
self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and
bubble on external leg (BEL) graphs.  It is always possible to express
an integrand in terms of cubic graphs, even for an even valency theory
like NLSM, by multiplying and dividing the integrand by factors of
inverse propagators.  Next, the ansatz must have the correct power
counting and external states, \emph{e.g.}, polarization vectors for
YM.  The numerator is assumed to be manifestly local but one approach
to finding color-dual numerators is to relax manifest locality, see
(...) for more details.

Jacobi relations are the heart of color-kinematics duality.
The color factors in an integrand obey a set of Jacobi identities.
Color-kinematics duality states that there exists a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
(Can trivially read off the adjoint color factors from a cubic graph.)
If any triplet of graphs is related by a Jacobi identity, so too must their numerators.
Broadly speaking there are two kinds of Jacobi identities:  \emph{defining} relations and \emph{boundary} relations.
Defining Jacobi relations can be used to express any graph in terms of a basis.
For example, the double box, crossed box, and penta-triangle are related to each other as follows
\be % [[11]]
\label{eq:TwoLoopJacobiOne}
\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0.
\ee
where the shared propagator is shown in red.
Using this relation the crossed box can be written (or \emph{defined}) in terms of the other two.
In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
(Any two of the double box, crossed box, and penta-triangle would suffice for a basis but the planar basis is chosen for simplicity in this work.)
For global color-kinematics duality each of the two basis graphs receives its own numerator ansatz and the numerator of any other graph can be expressed in terms of these.

After using the defining Jacobi relations to relate any graph to the basis, we will refer to any remaining Jacobi relations as boundary relations.
In other words, boundary relations (indirectly) relate basis elements to themselves.
For example, the crossed box numerator is related to itself via the following Jacobi relation
\be % [[19]]
\label{eq:TwoLoopJacobiTwo}
\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
\ee
where the shared propagator is shown in red as before.
Each of the crossed box numerators can be represented in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator ansatze.
While defining Jacobi relations simplify how many numerators require ansatze, boundary relations place restrictions on those ansatze.
In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
One option is to force the numerators of these graphs to zero.
However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
See (4 loop N=4 paper) for a discussion of BELs in the context of color-kinematics duality.

@@

Want explicit Bose sym, broken in many cases.

The second key constraint in an ansatz construction of color-dual numerators comes from graph symmetries.
Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
While it is very convenient to impose graph symmetries, it is not completely necessary in order to perform the double copy.
At tree level, finding manifestly color-dual numerators is often achieved at the expense of manifest Bose symmetry (see YZ theory, j-theory, Alex numerators from CHY, Henrik numerators).
Nonetheless, for a pure ansatz construction it is very reasonable to impose graph symmetries.
Note that the graph symmetry constraint is imposed on \emph{every} graph, not just the basis graphs.
%For example, the symmetries of the crossed box are spanned by
%\be
%\CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{3}{4} \text{ and } \CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{4}{3}
%\ee
For example, the symmetries of the crossed box
\be
\CrossedBoxGraphSym{1}{2}{3}{4}
\ee
are spanned by $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
In general, internal edge labels will have to be tracked as well.
Care must be taken with the signs in a symmetry relation.
To compensate for the antisymmetric structure of $f^{abc}$, the vertices are all totally antisymmetric and hence have signs built into their orientations.
Once the signs are included in the symmetry relations, the crossed box can be expressed in terms of the double box and penta-triangle, thus imposing non-trivial constraints on the ansatz.

@@

The last key source of constraints comes from ensuring that the ansatz
correctly reproduces the generalized unitarity cuts of the theory.
Matching the unitarity cuts provides the vast majority of
theory-dependent information for the ansatz by ensuring that the
numerators under construction are actually a valid representation of
the theory being considered.  Generalized unitarity methods has been
reviewed in many places \cite{BCFUnitarity, BernHuangReview,
  Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ,
  Bern:2012uf, BCJreview, Edison:2022jln} \ace{Here is a semi-random
  collection of unitarity-related citations.  Probably want to bulk it
  up a bit more} so we will be light on details here. We also want to
call special attention to Ref.~\cite{Carrasco:2023qgz} for a recent
treatment of unitarity methods optimized for even multiplicity
theories like NLSM.

In the context of loop integrand construction, generalized unitarity
allows us to equate products of on-shell tree amplitudes, encoded via
a graph $\gamma$, to sums over compatible\footnote{A diagram $g$ is compatible with the
  cut diagram $\gamma$ if $g$ is isomorphic to $\gamma$ or to any of
  the additional factorization channels of $\gamma$. } diagram
numerators evaluated on the support of the on-shell conditions and
weighted by their uncut propagators
\begin{equation}
\label{eq:SchematicCutEquation}
\text{Cut}[\gamma]= \sum_{\substack{\text{states}\\\text{crossing } E(\gamma)}} \prod_{v \in V(\gamma)} \atree(v)
= \sum_{g \text{ compat } \gamma}
\frac{n[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
 \, ,
\end{equation}
where $V(\gamma)$ are the vertices of $\gamma$ and $E(\gamma)$ its
edges.  The sum over states hides much of the complexity of cut
construction: for scalars the process is trivial while spinning states
greatly complicate matters (see
Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
and detailed examples of evaluating state sums).  It is useful to
provide some examples of the two types of expressions appearing in
\cref{eq:SchematicCutEquation}.  First the so-called
iterated unitarity cut, which can be written in the product-of-trees
representation as
\begin{equation}
  \label{eq:example-cut-prod}
  \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4) \,,
\end{equation}
or in reference to a collection of diagram numerators as
\begin{align}
  \label{eq:example-cut-sum}
  \ExCutLabeled{1}{2}{3}{4} &=
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}{(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7})^2}
  \ n\left[
    \IUCContrib{1}{4}{3}{2}
                              \right] \notag \\
  &\quad + 
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}
    {(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7'})^2}
  \ n\left[
    \IUCContrib{1}{3}{4}{2}
    \right] + 25\text{ others.}
\end{align}
When drawing cut diagrams, we will use gray blobs as in the left-hand
sides of \cref{eq:example-cut-prod,eq:example-cut-sum} and all drawn
legs are assumed to be on-shell.  When drawing numerator contributions
to cuts, we will not use blobs on vertices, and will use
\textcolor{cut-color}{dashed lines} bisecting edges to denote cut
lines and use colored edges to highlight the
\textcolor{ucp-color}{uncut propagators}.  From now on we will leave
the cut $\delta(\ell^2)$s implicit.

In color-charged theories, both sides of the cut can be further
decomposed according to the color algebra.  For theories charged under
the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
convenient to project onto a specific element of the Del
Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
inserting color-ordered amplitudes in the product of trees, and
restricting the set of compatible diagrams to those whose color
factors reduce to the appropriate DDM element when summing over
\emph{only the uncut color contractions}.  In this situation, the
color becomes an overall factor on the entire equality and thus can be
ignored.  Cuts that are organized in this manner are known as
``color-ordered'' cuts, in the same sense as color-ordered tree
amplitudes.  Since the DDM basis (and dual Kleiss-Kuijf amplitude
basis \cite{Kleiss:1988ne}) have $(n-2)!$ elements, one generally
needs to evaluate that many separate color-orderings of the same cut.
As an example, consider the ``kissing triangle'' cut topology, one of
the factorization channels of the iterated unitarity cut, which has
two topologically distinct color-ordered expansions
\begin{equation}
  \label{eq:kt-color-ord}
   \NMCutC =
  \begin{cases}
     s\text{-}t \text{ channel}
    &
      \frac{1}{\textcolor{ucp-color}{s_{12}}}
      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]\\
    t\text{-}u \text{ channel}
    & 
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
      n\left[
      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
      \right]
  \end{cases}
\end{equation}
which serve as a complete basis for the full cut.

>>>>

\def\tree{{\rm tree}}
\def\pol{\varepsilon}
\def\Tr{\, {\rm Tr}}
\def\tr{\, {\rm tr}}
\def\eps{\varepsilon}
\def\e{\varepsilon}
\def\ep{\varepsilon}
\def\SYM{MSYM}
\def\nn{\nonumber}
\def\Neqfour{{{\cal N}=4}}
\def\NeqFour{{{\cal N}=4}}
\def\Neqeight{{{\cal N}=8}}
\def\NeqEight{{{\cal N}=8}}
\def\NeqOne{{{\cal N}=1}}
\def\Fact{{\cal F}}
\def\f{\widetilde f}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}
\def\Ksl{{\s K}}
\def\ksl{\s{k}}
\def\Perm{{\cal P}}
\def\M{{\cal M}}
\def\ve{\varepsilon}
\def\tlambda{{\tilde\lambda}}
\def\MHVbar{$\overline{\hbox{MHV}}$}
\def\NMHVbar{$\overline{\hbox{NMHV}}$}
\def\P{{\rm P}}
\def\NHP{{\rm NHP}}
\def\mud{\lambda}
\def\bowtie{{\rm bow\mbox{-}tie}}
\newcommand{\cred}{\bf \color{red}}
 \newcommand{\cblue}{\color{blue}}
\newcommand{\andd}{\ , \quad \text{and}  \quad}
\newcommand{\forr}{\ , \quad \text{for}  \quad}
\newcommand{\ansatze}{ans\"atze} %Because words are hard

%TODO-type commands
\newcommand{\citepls}[1]{{\bf\color{red}[[Cite Needed: #1]]}}
\newcommand{\sect}{\textbf{\textcolor{red}{RefSec}}}

@@

Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
The four conditions we impose on an ansatz are summarized here and elaborated on below.\footnote{The four ansatz conditions are similar to those of Ref.~\cite{Bern:2015ooa} except that the authors demand that the numerators have the same loop power counting as Feynman gauge Feynman rules.  This is an additional assumption that is most emphatically not made here.}
\begin{enumerate}
\item \textbf{Locality}: Diagram numerators are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are only a function of the diagram's topology and labeling.  Furthermore, the diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
\end{enumerate}

In order to clarify general statements, the following subsections include examples from a 4pt 2-loop integrand for some color-dual theory like YM or NLSM.
This is the simplest integrand that demonstrates the full machinery of the color-dual bootstrap.
All tree and 1-loop processes are generated by single basis diagrams (the half ladder and $n$-gon respectively) so they lack examples of the ``boundary'' Jacobi relations to be described shortly.
Choosing the 4pt 2-loop integrand also has the advantage that this process appears prominently in this paper.

@@

The kinematic numerators must be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
Insisting on a local numerator is partly a matter of convenience as the ansatz for a rational function would quickly grow out of control without a guiding principle for what terms to include.
Locality is also physically motivated since Feynman rules typically produce polynomial numerators.
While these assumptions are well motivated from a physical and complexity standpoint, the literature has featured numerators that violate locality, modify naive power counting through the inclusion of higher spin modes, and break manifest Lorentz invariance \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}.
These developments suggest that relaxing locality is a viable alternative when the condition proves too stringent for an ansatz.
We will comment more on locality in \sect{}.

\jm{The next section feels a little redundant and silly sometimes because the integrand, color factors, kinematic numerators, etc. were defined a while ago.  I'm not sure how to merge the two sections though.}

@@

Color-kinematics duality is a statement about color factors, kinematic numerators, and the accompanying Jacobi relations.
Adjoint-type color factors are associated with cubic graphs, so satisfying color-kinematics duality implicitly requires expressing the integrand in terms of such graphs.
As mentioned earlier, this is possible to do even for a theory with quartic (or higher multiplicity) vertices by multiplying and dividing by propagators.
In the case of the 4pt 2-loop example promised above, there are 14 cubic graph topologies (shown in Fig \sect{}) ignoring tadpoles and bubble on external leg (BEL) graphs.

With the integrand expressed in terms of cubic graphs, it is possible to discuss the main ingredient in color-kinematics duality -- the Jacobi relations.
The color factors in an integrand obey a set of Jacobi identities.
Color-kinematics duality states that there \emph{exists} a way of writing the kinematic numerators of the integrand so that they obey the same set of Jacobi identities.
The Jacobi identities can be divided into two categories:  \emph{defining} relations and \emph{boundary} relations.
Defining Jacobi relations can be used to express any graph in terms of a basis.
For example, the double box, crossed box, and penta-triangle are related to each other as follows
\be % [[11]]
\label{eq:TwoLoopJacobiOne}
\JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle =0,
\ee
where the shared propagator is shown in red.
Using this relation the crossed box can be written (or \emph{defined}) in terms of the other two.
In this way, all of the 14 cubic 4pt 2-loop topologies can be written in terms of a basis of the double box and penta-triangle.
(Any two of the double box, crossed box, and penta-triangle would suffice for a basis but the planar basis is chosen for simplicity in this work.)
The numerator of each of the two basis graphs receives its own ansatz and the numerator of any other graph can be expressed in terms of these two.

After using the defining Jacobi relations to relate every graph to the basis, any remaining Jacobi relations will be referred to as boundary relations.
In other words, boundary relations (indirectly) relate basis elements to themselves.
For example, the crossed box numerator is related to itself via the following Jacobi relation
\be % [[19]]
\label{eq:TwoLoopJacobiTwo}
\JacobiTwoCrossedBoxOne + \JacobiTwoCrossedBoxTwo +  \JacobiTwoCrossedBoxThree =0,
\ee
where the shared propagator is shown in red as before.
Each of the crossed box numerators can be written in terms of the double box and penta-triangle so this Jacobi relation places constraints on the basis numerator \ansatze{}.
While defining Jacobi relations simplify how many numerators require \ansatze{}, boundary relations place restrictions on those \ansatze{}.
In principle there could be Jacobi relations involving tadpoles and BEL graphs, which would be subtle to handle.
One option is to force the numerators of these graphs to zero.
However, since these graphs will not contribute to physical unitarity cuts, we take a different approach.
These graphs are allowed to have non-zero numerators but any Jacobi relations involving them are simply not imposed or solved.
See Ref.~\cite{Bern:2012uf} for a discussion of BELs in the context of color-kinematics duality.

What has just been described is sometimes referred to as ``global'' color-kinematics duality because the Jacobi identities are solved by a single (global) integrand with off-shell internal lines.
In order to perform the double copy it is enough to simply satisfy the Jacobi identities on the generalized unitarity cuts, meaning that each graph can be assigned its own ansatz \cite{Bern:2015ooa}.
If a global solution cannot be found, this is one way to enlarge the ansatz where the other option described above was to incorporate non-local terms in the ``numerators''.
A globally color-dual integrand is desirable because of its simplicity and because a color-dual Lagrangian would naively produce precisely this object.

@@

Every numerator is required to respect all of the symmetries (or automorphisms) of its associated graph.
Graph symmetries are an avatar of Bose symmetry.
For a pure ansatz construction it is very reasonable to impose graph symmetries, but color-kinematics duality at tree-level is often achieved at the expense of manifest Bose symmetry \cite{Cheung:2016prv, Cheung:2021zvb, Brandhuber:2021bsf} \citepls{Alex numerators from CHY}.
In an ansatz construction graph symmetries are imposed for \emph{every} graph, not just the basis graphs.
%For example, the symmetries of the crossed box are spanned by
%\be
%\CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{3}{4} \text{ and } \CrossedBoxGraphSym{1}{2}{3}{4} \sim \CrossedBoxGraphSym{2}{1}{4}{3}
%\ee
For example, the symmetries of the crossed box
\be
\CrossedBoxGraphSym{1}{2}{3}{4}
\ee
are spanned by $\{1234\} \to \{2134\}$ and $\{1234\} \to \{1243\}$.
In general, internal edge labels must be tracked as well.
Furthermore, care must be taken with the signs in a symmetry relation.
To compensate for the antisymmetric color factors, $f^{abc}$, graph vertices are all totally antisymmetric and hence have signs built into their orientations.
Once the signs are included in the symmetry relations, the crossed box can be expressed in terms of the double box and penta-triangle, thus imposing non-trivial constraints on the ansatz.

@@

The final constraints comes from ensuring that the ansatz correctly reproduces the generalized unitarity cuts of the desired theory, thus guaranteeing that the numerators encode the correct physical, theory-dependent information.
Generalized unitarity methods has been reviewed in many places so we will be light on details here \cite{BCFUnitarity, BernHuangReview, Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ, Bern:2012uf, BCJreview, Edison:2022jln}.
\ace{Here is a semi-random collection of unitarity-related citations.  Probably want to bulk it up a bit more.}
Recently, generalized unitarity was optimized for even-multiplicity theories like NLSM \cite{Carrasco:2023qgz}.

Generalized unitarity equates products of on-shell tree amplitudes, encoded via
a graph $\gamma$, to sums over compatible\footnote{A diagram $g$ is compatible with the
  cut diagram $\gamma$ if $g$ is isomorphic to $\gamma$ or to any of
  the additional factorization channels of $\gamma$. } diagram
numerators evaluated on the support of the on-shell conditions and
weighted by their uncut propagators
\begin{equation}
\label{eq:SchematicCutEquation}
\text{Cut}[\gamma]= \sum_{\substack{\text{states}\\\text{crossing } E(\gamma)}} \prod_{v \in V(\gamma)} \atree(v)
= \sum_{g \text{ compat } \gamma}
\frac{n[g] \vert_\text{cut}}{\prod \limits_{\text{uncut}} \ell^2}
 \, ,
\end{equation}
where $V(\gamma)$ are the vertices of $\gamma$ and $E(\gamma)$ its
edges.  The sum over states hides much of the complexity of cut
construction: for scalars the process is trivial while spinning states
greatly complicate matters (see
Refs.~\cite{Kosmopoulos:2020pcd,Edison:2022jln} for recent discussion
and detailed examples of evaluating state sums).
As an example of the two types of expressions appearing in \cref{eq:SchematicCutEquation}, consider the so-called iterated two-particle cut which can be represented as a product of trees via
\begin{equation}
  \label{eq:example-cut-prod}
  \ExCutLabeled{1}{2}{3}{4} = \!\!\!\!\! \sum_{\substack{\text{states of }\\ \{\ell_1, \ell_2, \ell_3, \ell_4\}}} \!\!\!\!\!\!\!
  \atree(1,2,\ell_1,\ell_2) \atree(-\ell_1,-\ell_2,\ell_3,\ell_4) \atree(-\ell_3,-\ell_4,3,4)
\end{equation}
or as a collection of diagram numerators via
\begin{align}
  \label{eq:example-cut-sum}
  \ExCutLabeled{1}{2}{3}{4} &=
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}{(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7})^2}
  \ n\left[
    \IUCContrib{1}{4}{3}{2}
                              \right] \notag \\
  &\quad + 
  \frac{\delta(\textcolor{cut-color}{\ell_1^2})
    \delta(\textcolor{cut-color}{\ell_2^2})
    \delta(\textcolor{cut-color}{\ell_3^2})
    \delta(\textcolor{cut-color}{\ell_4^2})}
    {(\textcolor{ucp-color}{\ell_5})^2
    (\textcolor{ucp-color}{\ell_6})^2
    (\textcolor{ucp-color}{\ell_7'})^2}
  \ n\left[
    \IUCContrib{1}{3}{4}{2}
    \right] + 25\text{ others.}
\end{align}
When drawing cut diagrams, we will use gray blobs as in the left-hand
sides of \cref{eq:example-cut-prod,eq:example-cut-sum} and all drawn
legs are assumed to be on-shell.  When drawing numerator contributions
to cuts, we will not use blobs on vertices, and will use
\textcolor{cut-color}{dashed lines} bisecting edges to denote cut
lines and use colored edges to highlight the
\textcolor{ucp-color}{uncut propagators}.  From now on we will leave
the cut $\delta(\ell^2)$s implicit.
\jm{Again, I love the colors!  Would it be possible to add $\ell$ labels to the RHS of \cref{eq:example-cut-sum} to show what $\ell_5$, $\ell_6$... are?}

In color-charged theories, both sides of the cut can be further
decomposed according to the color algebra.  For theories charged under
the adjoint of $SU(N)$ via $f^{abc}$-dressed amplitudes, it is
convenient to project onto a specific element of the Del
Duca-Dixon-Maltoni (DDM) color basis \cite{DixonMaltoni} by only
inserting color-ordered amplitudes in the product of trees, and
restricting the set of compatible diagrams to those whose color
factors reduce to the appropriate DDM element when summing over
\emph{only the uncut color contractions}.  In this situation, the
color becomes an overall factor on the entire equality and thus can be
ignored.  Cuts that are organized in this manner are known as
``color-ordered'' cuts, in the same sense as color-ordered tree
amplitudes.  Since the DDM basis (and dual Kleiss-Kuijf amplitude
basis \cite{Kleiss:1988ne}) have $(n-2)!$ elements, one generally
needs to evaluate that many separate color-orderings of the same cut. \jm{Don't you need $(n-2)!$ for each blob in the cut?  So you need to evaluate $(n_1-2)! (n_2-2)!...$ cuts where $n_1$, $n_2$... are the multiplicities of the blobs.}
As an example, consider the ``kissing triangle'' cut topology -- one of
the factorization channels of the iterated unitarity cut -- which has
two topologically distinct color-ordered expansions
\begin{equation}
  \label{eq:kt-color-ord}
   \NMCutC =
  \begin{cases}
     s\text{-}t \text{ channel}
    &
      \frac{1}{\textcolor{ucp-color}{s_{12}}}
      n \left[\scalebox{0.65}{\KTBTContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]\\
    t\text{-}u \text{ channel}
    & 
      \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
      n \left[
      \scalebox{0.65}{\KTDBContrib{1}{4}{3}{2}}
      \right]
      +
      \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
      n\left[
      \scalebox{0.65}{\KTDBContrib{1}{3}{4}{2}}
      \right]
  \end{cases}
\end{equation}
which serve as a complete basis for the full cut.
